Predicting Which States are Most Interested in the term *China Virus* Based off Identity Politics, Demography and COVID-19 Statistics 

### 2020-05-05 Final-Draft.Rmd
changes

##mcmc_ stable

@@

@@

##mcmc_ stable

@@

@@

##mcmc_ stable

@@

## 4.4 Model 4 Evaluation (Longitudinal)

##mcmc_ stable

@@

```{r}
#Repeated Measures
set.seed(454)
pred_1 <- posterior_predict(
  RM_model,
  newdata = model_data, transform = TRUE)

@@

```{r}
#Normal Regression
set.seed(454)
pred_2 <- posterior_predict(
  NR_model,
  newdata = model_data, transform = TRUE)

@@

```{r}
#Repeated Measures + Normal Regression
set.seed(454)
pred_3 <- posterior_predict(
  model_2,
  newdata = model_data, transform = TRUE)

@@

```{r}
#Longitudinal Model
set.seed(454)
pred_4 <- posterior_predict(
  complexmod,
  newdata = model_data, transform = TRUE)

@@

## 5.1 Posterior Predctions All States

@@

>>>>

##mcmc plots
```{r}
mcmc_trace(RM_model, pars = c("(Intercept)","Sigma[State:(Intercept),(Intercept)]"))
mcmc_dens_overlay(RM_model, pars = c("(Intercept)","Sigma[State:(Intercept),(Intercept)]")) 
```

As we can see in this mcmc trace plot, it looks like our MCMC is fairly stable but could do with a bit more stability as we see that the peaks are spread around the 40-42.5 range. We also see that our values for $\sigma_b^2$ is greater than 0, our value of sigma is around 75 meaning that we must include random intercepts in our final model

@@

```{r}
pp_check(RM_model, nreps=50)
```

Overall, we can see that our repeated measures model it tells us that the structure of our model is fairly reasonable, In other words, the assumption of using a normal model is fairly reasonable outside of the fact that the tails are a bit thicker than we would want them to be. This is because we are expecting a lot of states that will have multiple days with zero value, if no one in the state looks up the term. This is why our tails are a bit thicker than we would want them to be, specially around 0.

@@

##mcmc plots

```{r}
# Trace plots
mcmc_trace(NR_model,pars = c("sigma","(Intercept)","percent_white","StateColorred","StateColorpurple","positive","Day"),facet_args = list(ncol = 3, strip.position = "left"))

# Density plots
mcmc_dens_overlay(NR_model, pars = c("sigma","(Intercept)","percent_white","StateColorred","StateColorpurple","positive","Day"),facet_args = list(ncol = 3, strip.position = "left"))
```
Compared to the previous model, it looks that our chains are more stable and they have closer peaks.

@@

```{r}
pp_check(NR_model, nreps = 50)
```

Although our posterior predictive check is pretty similar to our previous model, we see that the peaks are a bit more closer together. And similar to the previous model the structure of the GLM is fairly reasonable.

@@

```{r}
mcmc_trace(model_3, pars=c("(Intercept)","percent_white","StateColorred","StateColorpurple","positive","Day","b[(Intercept) State:AK]","b[(Intercept) State:WA]"),facet_args = list(ncol = 3, strip.position = "left"))

mcmc_trace(model_3, pars = c("sigma","Sigma[State:(Intercept),(Intercept)]"))

mcmc_dens_overlay(model_3, pars = c("(Intercept)","percent_white","StateColorred","StateColorpurple","positive","Day","b[(Intercept) State:AK]","b[(Intercept) State:WA]"),facet_args = list(ncol = 3, strip.position = "left"))

mcmc_dens_overlay(model_3, pars = c("sigma","Sigma[State:(Intercept),(Intercept)]"))
```

Compared to the previous model, we see that our chains are more stable for the intercept and the percent_white variables as the peaks are closer together. We also see that our $\sigma_b^2$ is almost always above 0, and the density has a mean around 75 similar to our repeated measures model.

##ppcheck
```{r}
pp_check(model_3, nreps=50)
```
As seen in our prior posterior predictive checks, they have similar errors around the tails. But it seems that our GLM structure is also reasonable for this model. 
## 4.4 Model 4 Evaluation (Longitudinal)

##mcmc plots

```{r}
# Trace plots
mcmc_trace(complexmod,pars = c("(Intercept)","percent_white","StateColorred","StateColorpurple","positive","Day","b[Day State:AK]","b[Day State:WA]"),facet_args = list(ncol = 3, strip.position = "left")) 
mcmc_trace(complexmod, pars = c("sigma"),regex_pars = "Sigma",facet_args = list(ncol = 2, strip.position = "left"))

# Density plots
mcmc_dens_overlay(complexmod, pars = c("(Intercept)","percent_white","StateColorred","StateColorpurple","positive","Day","b[Day State:AK]","b[Day State:WA]"),regex_pars = "Sigma",facet_args = list(ncol = 4, strip.position = "left"))

mcmc_dens_overlay(complexmod, pars = c("sigma"),regex_pars = "Sigma",facet_args = list(ncol = 2, strip.position = "left"))
```

In the dens overlay we can see that our value for $\sigma_{1b}^2$ is close to zero we could argue that random slopes are not necessary, but the mean of  $\sigma_{1b}^2$ is around 2-2.5. Similar to our previous dens overlay checks our value of $\sigma_b^2$ is almost always above zero and its mean is around 75, which means that random intercepts are necessary.

@@

```{r}
pp_check(complexmod, nreps = 50)
```
Overall all ppchecks tend to have the similar graph because we are assuming a normal relationship on the response variable for all of them.

@@

```{r, message=FALSE, include=FALSE}
#Repeated Measures
set.seed(454)
pred_1 <- posterior_predict(
  RM_model,
  newdata = model_data, transform = TRUE)

@@

```{r, message=FALSE, include=FALSE}
#Normal Regression
set.seed(454)
pred_2 <- posterior_predict(
  NR_model,
  newdata = model_data, transform = TRUE)

@@

```{r, message=FALSE, include=FALSE}
#Repeated Measures + Normal Regression
set.seed(454)
pred_3 <- posterior_predict(
  model_3,
  newdata = model_data, transform = TRUE)

@@

```{r, message=FALSE, include=FALSE}
#Longitudinal Model
set.seed(454)
pred_4 <- posterior_predict(
  complexmod,
  newdata = model_data, transform = TRUE)

@@

## 5.1 Posterior Predictions All States

@@

As we can see in the table above, the lowest mae was achieved by our most complex model, Model 4 which allowed for both random slopes and random intercepts. But the mae value is not that different from the mae acchieved by Model 3 which was more simple allowing only for random intercepts. Interestingly Model 1 our simplest model had a higher proportion of the data falling within the 95% posterior predictive interval.

### Why we chose Model 3 as our best model?

We believe that the decreases in mae and increases of the proporiton of values observed within 50% of the posterior predictive interval do not justify increasing the complexity. Which is why we argue that Model 3 is the best model because it acchieves similar results to model 4 without making it computationally expensive. But if we want a more precise model we would use Model 4.
